Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-09-20 ms.tex
added a comparison of the nint=4 versus nint=1 cases.

>>>>

\clearpage
\subsubsection{Co-added Versus Un-coadded data}\label{sec:coadds}
In Figure \ref{fig:coaddedData}, we compare data that was taken in READ mode.
In this case, there were 1000 integrations with a 2048x256 stripe illuminated with the lamp on all four detectors.
In the case of NFRAME=4, the data are co-added with bit-shift operations whereas for NFRAME=1, all data is used.
There are 2 groups with NFRAME=4 and 8 groups with NFRAME=1.
The primary difference between the two are
\begin{itemize}
\item the reference pixel correction is performed on frame-by-frame basis for NFRAME=1 and on a co-added group of 4 for NFRAME=4
\item the slope is calculated with all 8 groups
\end{itemize}.
This differences did not have a large overall impact on stability of the lightcurves.

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_azlab06_baseline3}{0.47\textwidth}{RAPID mode with NFRAME=1}
\fig{azlab_ratio_tser_azlab06_nint4.pdf}{0.47\textwidth}{Co-added with NFRAME=4}}}
\caption{Co-added with NFRAME=4 versus 8 groups RAPID data.
Using reference pixel subtraction on the individual reads in RAPID mode does not substantially improve the ratio time series of the two detectors as compared with co-added data where reference pixel correction was applied to the group (which is an average of the 4 frames).}\label{fig:coaddedData}
\end{figure*}
